---
title: "Basic SUmmary Stats"
author: "Jacob Grippin"
date: "1/14/2020"
output:
  html_document:
    df_print: paged
---
## Introdouction
```{r preparations, include=FALSE}
#Easier reference variable names in mtcars dataset
attach(mtcars)
#Store column names of dataset as a new object
names = colnames(mtcars)

changend <- table(vs)
#Help documentation for subset command
#?subset
vs0 <- subset(mtcars, vs == 0)
vs1 <- subset(mtcars, vs == 1)
#Help documentation for t.test command
#?t.test
testres <- t.test(vs0$mpg, vs1$mpg)
```

This is a short *memo*. Describing a dataset, showing some visuals. Put 2 spaces at end of line for output to go to next line.  

Load system dataset "mtcars". Column names of dataset included below.    
**`r colnames(mtcars)` **


### Variable Descriptions 
I am interested in variables for Miles Per Gallong(MPG) and VS. Their variable information is included below.  
Variable `r names[8]` has the following frequency counts.   
0         1  
`r changend`  

Variable `r names[1]` has the following measure of mean and standard deviation.  
**mean = **`r mean(mtcars$mpg)`  
**standard deviation **= `r sd(mtcars$mpg)`  

```{r ttest, include=FALSE, echo=FALSE}
#Commands below to compare avg mpg for vs equal to 0 and equal to 1. 
vs0 <- subset(mtcars, vs == 0)
vs1 <- subset(mtcars, vs == 1)
sink("../../static/Results/ttest.txt")
testres <- t.test(vs0$mpg, vs1$mpg)
#Print t.test results
testres
sink()
```
  

Following links have good reference information:  
[Rmarkdown Webiste](https://rmarkdown.rstudio.com/) - tutorial rmarkdown  
[Rmarkdown cheatsheet](https://rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf) - cheatsheet 



